A Tutorial on Tailored Simulation-Based Power Analysis for Experimental Designs with Generalized Linear Mixed Models

### 2023-09-18 docs/manuscript.Rmd
last edits for preprint publication

note: "\\clearpage" #added this to move entire author note to second page
authornote: |
  This research was funded by a grant from the Volkswagen Foundation (Grant No. 98525).
  All R code in this manuscript and simulation results are available in the project's repository on the Open Science Framework (OSF): https://osf.io/dhwf4/

@@

wordcount         : "7598"

@@

floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no

>>>>

note: "\\clearpage" #added this to move entire author note to second page
authornote: |
  This research was funded by a grant from the Volkswagen Foundation (Grant No. 98525).
  All materials (reproducible manuscript incl. R code, simulation results) are available in the project's repository on the Open Science Framework (OSF): https://osf.io/dhwf4/

@@

wordcount         : "7600"

@@

floatsintext      : yes
linenumbers       : no
draft             : no
mask              : no
